Survival Probability Difference M-F

### 2025-04-24 code/R/Survival_by_sex.Rmd
Initial commit of M-F survival probability

# laod the model with sex as a covariate of survival
mod <- readRDS("/Users/johnimperato/Desktop/Mossy-Pond_companion/sex_survival_covariate_model.rds")

@@

@@

# Create the plot
difference_plot <- ggplot(time_summaries_df, aes(x = primary_period, y = mean)) +
  geom_point(color = "blue", size = 2) +  # Increased point size for better visibility
  geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.2, color = "blue") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(
    title = "Difference in Survival Probabilities (M - F) Between Primary Periods",
    x = "Primary Period",
    y = "Difference in Survival Probability"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for readability
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold")  # Center and style the title
  ) +
  # Correct the x-axis limits to match 'primary_period' labels
  scale_x_discrete(limits = levels(time_summaries_df$primary_period))

@@

# Save the plot to a file
ggsave("/Users/johnimperato/Desktop/Mossy-Pond_companion/difference_in_survival_probabilities.png", 
       plot = difference_plot, width = 10, height = 6, dpi = 300)
```

>>>>

# laod the model with sex as a covariate of survival
mod_sex <- readRDS("/Users/johnimperato/Desktop/Mossy-Pond_companion/sex_survival_covariate_model_4.rds")

@@

View(time_summaries_df)

@@

# Create the plot
difference_plot <- ggplot(time_summaries_df, aes(x = primary_period, y = mean)) +
  geom_point(color = "blue", size = 2) +  # Increased point size for better visibility
  geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.2, color = "blue") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(
    title = "Difference in Survival Probabilities (M - F) Between Primary Periods\nsurvival_fill_value = 'M'",
    x = "Primary Period",
    y = "Difference in Survival Probability"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for readability
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold")  # Center and style the title
  ) +
  # Correct the x-axis limits to match 'primary_period' labels
  scale_x_discrete(limits = levels(time_summaries_df$primary_period))

@@

# Save the plot to a file
ggsave("/Users/johnimperato/Desktop/Mossy-Pond_companion/difference_in_survival_probabilities_M_fill.png", 
       plot = difference_plot, width = 10, height = 6, dpi = 300, bg = "white")
```
